### 2024-06-25 correlation.qmd
20240618 - NHST
20240625 - correlation

@@

@@

>>>>

## Overview of Correlation {#sec-correlationOverview}

Correlation is a metric of the association between variables.
Covariance is the association between variables and in an unstandardized metric that differs for variables with different scales.
By contrast, correlation is in a standarized metric that does not differ for variables with different scales.
When examining the association between variables that are [interval](#sec-interval) or [ratio](#sec-ratio) levels of measurement, Pearson correlation is used.
When examining the association between variables that are [ordinal](#sec-ordinal) in level of measurement, Spearman correlation is used.

@@

The formula for the correlation coefficient\index{correlation} is in @eq-pearsonCorrelation.

@@

Interactive visualizations by Kristoffer Magnusson on *p*-values and null-hypothesis significance testing are below:

- <https://rpsychologist.com/correlation/> (archived at <https://perma.cc/G8YR-VCM4>)

## Examples {#sec-correlationExamples}

### Covariance {#sec-correlationExamplesCovariance}

### Pearson Correlation {#sec-correlationExamplesPearson}

### Spearman Correlation {#sec-correlationExamplesSpearman}

### Nonlinear Correlation {#sec-correlationExamplesNonlinear}

### Correlation Matrix {#sec-correlationExamplesMatrix}

### Correlogram {#sec-correlationExamplesCorrelogram}
